Why do we Eval?\\\Large A large-scale study of Eval usage in R

### 2021-03-18 analysis/normalized.Rmd
Improvements

Minimized:
```{r}
widespread_minimized <- E_cano %>%
  group_by(minimized) %>%
  summarize(n_call_sites = n_distinct(src_ref), proportion = ratio(n_call_sites, nb_call_sites), n_packages = n_distinct(ev_package), n_operations = round(mean(n_op, na.rm=TRUE), 2), percent_envir = ratio(n_distinct(cur_data()$src_ref[!is.na(cur_data()$envir)]),  n_call_sites)) %>% 
  arrange(desc(n_call_sites))

>>>>

Minimized:
```{r}
widespread_minimized <- E_cano %>%
  group_by(minimized) %>%
  summarize(n_call_sites = n_distinct(src_ref), proportion = ratio(n_call_sites, nb_call_sites), n_packages = n_distinct(ev_package), n_operations = round(mean(n_op, na.rm=TRUE), 2), percent_envir = ratio(n_distinct(cur_data()$src_ref[!is.na(cur_data()$envir)]),  n_call_sites), percent_envir_calls = ratio(sum(!is.na(envir)), n())) %>% 
  arrange(desc(n_call_sites))

### 2021-03-18 paper/main.tex
Improvements

Similarly, when a function is evaluated on some variable (\c{F(X)} minimized expression), the percentage of non default environment is high, \packageMinimizedpercentenvird\%.

>>>>

% the percentage of non-default environment is more convincing when looking at the number of calls rather the number of sites

Similarly, when a function is evaluated on some variable (\c{F(X)} minimized expression), the percentage of non default environment is rather high, \packageMinimizedpercentenvird\%.
